---
title: "Activity: Street or Road?"
author: "Neeraj Thokala"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 
library(dplyr)
library(ggplot2)

#load in the data here 
# we will only be using the "street-addresses.csv" file from the text

read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")

```

## Recreate Solved Example using `sample(50)`

```{r}
Addresses <- read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")
Sample <- 
  Addresses %>%
  sample_n(size = 50)

```

## Recreate Soved Example using the entire `Address` data set

```{r}


```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}
Matches <- 
  Sample %>%
  filter(grepl(pattern = "PO", pattern = "NCSU", address))

```

Over 100 addresses


## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

We are looking for address that start with St or Rd / Road, and then we create a new function called leftovers, where within the Addresses dataset we filter out all the address with the appropriate appartment unit and adress as well as the Box number for each particualar address that is filtered out from the data set. The appartment and unit number is wanted, therefore the regex includes an identifier for the number inside extraction parentheses.

#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}



```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}
library(dplyr)

Addresses %>% arrange(desc(pop))

```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}
library(dplyr)
library(ggplot2)

Addresses %>%
  filter(desc(pop))

ggplot(Addresses, aes(x = popularity, y = streetname)) +
  geom_point()
```

#### Additional Question 3: Comment on any patterns you see

I noticed that while some street names are more popular than others, there is no specific correlation between what names are popular and what names aren't meaning there is no clear cut way to predict what street names will be most popular going forward.
